Design and Implementation of a Multithreaded Virtual Machine for Executing Linear Logic Programs

### 2014-07-25 related_work.tex
Fixed.
More data

>>>>

Several linear logic programming languages have been developed in the past~\cite{Miller85anoverview}.
Lolli, a programming language based on a fragment of intuitionistic linear logic~\cite{Hodas94logicprogramming}, 
proves goals by lazily managing the context of linear resources during backward-chaining proof search.
LolliMon~\cite{Lopez:2005:MCL:1069774.1069778} is a concurrent linear logic programming language that integrates
both forward and backward-chaining search, where the backward-chaining phase is done sequentially but
the forward-chaining is done concurrently inside a monad. The backward-chaining phase is suspended
between the forward-chaining phases, where a fix-point is computed.
LolliMon is derived from the concurrent logical framework called CLF~\cite{Watkins:2004uq}.
